Draft

### 2024-07-04 Bootstrap.Rmd
BCa works

```{r}
## WARNING:
## Useless function for now!

# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
bcanon <- function(x,bootsam,theta,...,alpha =
                     c(.025,.05,.1,.16,.84,.9,.95,.975)) { 
    if (!all(alpha < 1) || !all(alpha > 0))
      stop("All elements of alpha must be in (0,1)")

    # alpha_sorted <- sort(alpha)
    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
    #   warning("nboot is not large enough to estimate your chosen alpha.")

    call <- match.call()
    # n <- length(x)
    n <- nrow(x)
    # thetahat <- theta(x,...)
    a <- c()
    for (i in 1:n) {
      a <- append(a, theta(x[i, 1], x[i, 2]))
    }
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

    nboot <- length(bootsam)/2
    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)

    # thetastar <- apply(bootsam,1,theta,...)
    thetastar <- c()
    for (c in 1:B) {
      a <- c()
      for (i in 1:n) {
        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
      }
      thetastar <- append(thetastar, sum(a/p))
    }
    thetastar <- sort(thetastar)

@@

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i]
        a <- c()
        for (j in 1:n) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
# bcanon(random_points,df_boot,circle_nb,alpha = .95)
# Produces an error
```

>>>>

```{r}
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(x,bootsam,theta,...,alpha =
                     c(.025,.05,.1,.16,.84,.9,.95,.975)) { 
    if (!all(alpha < 1) || !all(alpha > 0))
      stop("All elements of alpha must be in (0,1)")

    alpha_sorted <- sort(alpha)
    if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
    warning("nboot is not large enough to estimate your chosen alpha.")

    call <- match.call()
    n <- nrow(x)
    a <- mapply(theta, x[, 1], x[, 2])
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

    nboot <- length(bootsam)/2
    thetastar <- c()
    for (c in 1:B) {
      a <- mapply(theta, bootsam[, (2*c)-1], bootsam[, 2*c])
      thetastar <- append(thetastar, sum(a/p))
    }
    thetastar <- sort(thetastar)

@@

    u <- rep(0,n)
    for(i in 1:n){
        x_i <- x[-i,]
        a <- c()
        for (j in 1:(n-1)) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
# Interval of intended coverage 1 - 2*alpha = .95 => alpha = .025
res <- bcanon(random_points,df_boot,circle_nb,alpha = c(.025, .975))
```

```{r}
cat("Un intervalle de confiance à 95% par la méthode BCa est : [", res$confpoints[1,2], ";", res$confpoints[2,2], "]")
```

### 2024-07-04 Bootstrap_draft.Rmd
BCa works

@@

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i]
        a <- c()
        for (j in 1:n) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
bcanon(random_points,df_boot,circle_nb,alpha = .95)
```

>>>>

```{r}
plot(density(est_boot_3))
```

@@

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i,]
        a <- c()
        for (j in 1:(n-1)) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

@@

```{r}
# Interval of intended coverage 1 - 2*alpha = .95 => alpha = .025
bcanon(random_points,df_boot,circle_nb,alpha = c(.025, .975))
# Error in if ((x >= x0F + r) & (x <= x1F - r) & (y >= y0F + r) & (y <=  : 
#  missing value where TRUE/FALSE needed
# Works!
```

#### Si alpha = 0.95

$confpoints
     alpha bca point
[1,]  0.95   42526.2

$z0
[1] 0.01504034

$acc
[1] 0.02810749

$u
  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
 [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
 [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
 [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
 [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
 [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
 [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
 [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
 [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
 [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28

$call
bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
    alpha = 0.95)

#### Si alpha = 0.25

$confpoints
     alpha bca point
[1,]  0.25  28520.57

$z0
[1] 0.01504034

$acc
[1] 0.02810749

$u
  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
 [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
 [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
 [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
 [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
 [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
 [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
 [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
 [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
 [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28

$call
bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
    alpha = 0.25)

#### Si alpha = c(0.025, 0.975)

$confpoints
     alpha bca point
[1,] 0.025  22154.37
[2,] 0.975  44308.74

$z0
[1] 0.01504034

$acc
[1] 0.02810749

$u
  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
 [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
 [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
 [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
 [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
 [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
 [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
 [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
 [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
 [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28

$call
bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
    alpha = c(0.025, 0.975))

```{r}
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)

alpha <- .95
x <- random_points
bootsam <- df_boot
theta <- circle_nb

    if (!all(alpha < 1) || !all(alpha > 0))
      stop("All elements of alpha must be in (0,1)")

    # alpha_sorted <- sort(alpha)
    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
    #   warning("nboot is not large enough to estimate your chosen alpha.")

    ### call <- match.call()
    # n <- length(x)
    n <- nrow(x)
    # thetahat <- theta(x,...)
    a <- c()
    for (i in 1:n) {
      a <- append(a, theta(x[i, 1], x[i, 2]))
    }
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

    u <- rep(0,n)

    i <- 1
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i,]
        a <- c()

        ## Bug dans cette boucle
        j <- 1
        for (j in 1:(n-1)) {
          print(j)
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

    confpoints <- quantile(x=thetastar,probs=tt,type=1)
    names(confpoints) <- NULL
    confpoints <- cbind(alpha,confpoints)
    dimnames(confpoints)[[2]] <- c("alpha","bca point")
    return(list(confpoints=confpoints, 
                z0=z0, 
                acc=acc, 
                u=u, 
                call=call))
```

### 2024-07-04 Draft/Draft.Rmd
BCa works

>>>>

# Bootstrap

## ABC-BCA

```{r}
## WARNING:
## Useless function for now!

# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
bcanon <- function(x,bootsam,theta,...,alpha =
                     c(.025,.05,.1,.16,.84,.9,.95,.975)) { 
    if (!all(alpha < 1) || !all(alpha > 0))
      stop("All elements of alpha must be in (0,1)")

    # alpha_sorted <- sort(alpha)
    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
    #   warning("nboot is not large enough to estimate your chosen alpha.")

    call <- match.call()
    # n <- length(x)
    n <- nrow(x)
    # thetahat <- theta(x,...)
    a <- c()
    for (i in 1:n) {
      a <- append(a, theta(x[i, 1], x[i, 2]))
    }
    # Estimated total thus obtained from the initial sample
    thetahat <- sum(a/p)

    nboot <- length(bootsam)/2
    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)

    # thetastar <- apply(bootsam,1,theta,...)
    thetastar <- c()
    for (c in 1:B) {
      a <- c()
      for (i in 1:n) {
        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
      }
      thetastar <- append(thetastar, sum(a/p))
    }
    thetastar <- sort(thetastar)

    z0 <- qnorm(sum(thetastar<thetahat)/nboot)

    u <- rep(0,n)
    for(i in 1:n){
        # u[i] <- theta(x[-i],...)
        x_i <- x[-i]
        a <- c()
        for (j in 1:n) {
          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
        }
        # Estimated total thus obtained from the initial sample
        u[i] <- sum(a/p)
    }
    uu <- mean(u)-u
    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)

    zalpha <- qnorm(alpha)

    tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))

    confpoints <- quantile(x=thetastar,probs=tt,type=1)
    names(confpoints) <- NULL
    confpoints <- cbind(alpha,confpoints)
    dimnames(confpoints)[[2]] <- c("alpha","bca point")
    return(list(confpoints=confpoints, 
                z0=z0, 
                acc=acc, 
                u=u, 
                call=call))
}
```

```{r}
# bcanon(random_points,df_boot,circle_nb,alpha = .95)
# Produces an error
```
